The Astropy Project

### 2017-10-27 main.tex
PyPI

\astropypkg is available from several of the Python distributions for scientific
% * <mattwcraig@gmail.com> 2017-10-27T07:13:51.093Z:
% 
% > \astropypkg i
% I changed a few of the macros in here to refer to the package rather than the project because it is the package being discussed here.
% 
% ^.
computing, such as Anaconda or Enthought Canopy, which include also some of
\astropy's affiliated packages.
Alternatively, \astropypkg can be readily installed from the Python Package Index
(PyPI) using pip, the recommended command-line tool for installing Python packages
that is included by default since Python 2 $\geq$ 2.7.9 and Python 3 $\geq$ 3.4.
For most recent \astropypkg releases, pre-built wheel distributions are obtainable
from PyPI for Windows, Mac OS X and Linux systems that provide faster
installation compared to the source distribution.  Optionally, the version of
the package and the dependencies needed to run or build the software are given
by a specifier to the pip package manager as described in PEP 440\footnote{For
more detailed installation instructions and optional flags see
\url{http://docs.astropy.org/en/stable/install.html\#installing-astropy}}.

>>>>

\astropypkg is available from several of the Python distributions for scientific
% * <mattwcraig@gmail.com> 2017-10-27T07:13:51.093Z:
% 
% > \astropypkg i
% I changed a few of the macros in here to refer to the package rather than the project because it is the package being discussed here.
% 
% ^.
computing, such as Anaconda or Enthought Canopy, which include also some of
\astropy's affiliated packages.
Alternatively, \astropypkg can be readily installed from the Python Package
Index\footnote{\url{https://pypi.python.org/pypi}} (PyPI) using pip, the
recommended command-line tool for installing Python packages
that is included by default since Python 2 $\geq$ 2.7.9 and Python 3 $\geq$ 3.4.
For most recent \astropypkg releases, pre-built wheel distributions are obtainable
from PyPI for Windows, Mac OS X and Linux systems that provide faster
installation compared to the source distribution.  Optionally, the version of
the package and the dependencies needed to run or build the software are given
by a specifier to the pip package manager as described in PEP 440\footnote{For
more detailed installation instructions and optional flags see
\url{http://docs.astropy.org/en/stable/install.html\#installing-astropy}}.
